---
title: "EPL Table Battle Royale"
---

```{r, child="_setup.Rmd"}
```

```{r banner, results='asis'}
cat(as.character(lock_banner()))
```

`r nrow(PLAYERS)` friends are predicting the order of the
`r CONFIG$season_label` Premier League table.
`r if (is_locked()) "Tables are fixed. The league now spends nine months telling them how wrong they were." else "Once the deadline passes their tables are fixed, and the league spends nine months telling them how wrong they were."`

---

## Leaderboard

```{r scoring-banner, results='asis'}
cat(as.character(scoring_banner(RES)))
```

```{r leaderboard}
render_leaderboard(RES)
```

```{r leaderboard-note, results='asis'}
if (!SEASON_STARTED) {
  cat("<p class='note'>No matches played yet — the league table is alphabetical",
      "until the first results land, so the columns below describe nothing",
      "meaningful so far.</p>")
}
cat("<p class='note'>", describe_method(), "</p>")
```

---

## Live Premier League table

```{r live-table}
render_live_table(LIVE)
```

<p class="note">
Champions League places shaded green, relegation places shaded red.
Data from `r provider_label(attr(LIVE, "provider"))`, last refreshed
**`r fmt_when(attr(LIVE, "fetched_at"))`**`r if (isTRUE(attr(LIVE, "stale"))) " — the most recent refresh attempt failed, so these numbers may be behind" else ""`.
</p>

---

## Every entrant, side by side

Rows are predicted finishing positions; each column is one entrant's sealed table.

```{r grid}
render_comparison_grid(RES, PLAYERS)
```

<p class="note">
Full per-entrant breakdowns, including how far off each pick currently is, are on
the [predictions page](predictions.html).
</p>
