---
title: "Make Your Picks"
---

```{r, child="_setup.Rmd"}
```

```{r banner, results='asis'}
cat(as.character(lock_banner()))
```

Drag the clubs into the order you think they will finish, or nudge them with the
arrows. Your draft saves in this browser as you go, so you can close the tab and
come back to it. When the table looks right, hit **Copy my code** at the bottom
and send that one line to Allen.

```{r inject, results='asis'}
# The club list and the deadline come from the same files the rest of the site
# uses, so the picker can never drift out of sync with data/teams.csv.
payload <- list(
  teams = lapply(seq_len(nrow(TEAMS)), function(i) {
    list(name = TEAMS$team[i], abbrev = TEAMS$abbrev[i], short = TEAMS$short_name[i])
  }),
  deadline = format(CONFIG$lock_time, "%Y-%m-%dT%H:%M:%S%z"),
  locked = is_locked()
)
cat("<script>\nconst PICKER_DATA = ",
    jsonlite::toJSON(payload, auto_unbox = TRUE), ";\n</script>\n", sep = "")
```

<!-- NOTE: this block must stay flush-left. Indenting raw HTML by four spaces
makes pandoc treat it as a markdown code block and render the controls as
escaped text instead of a form. -->
<div id="picker">
<div class="picker-row">
<label for="entrant"><strong>Your name</strong></label>
<input type="text" id="entrant" placeholder="e.g. Allen Brown" autocomplete="name">
</div>
<div class="picker-actions">
<button type="button" class="btn-secondary" id="btn-shuffle">Shuffle</button>
<button type="button" class="btn-secondary" id="btn-alpha">A–Z</button>
<button type="button" class="btn-secondary" id="btn-reset">Start over</button>
<span class="picker-status" id="save-status"></span>
</div>
<ol id="club-list" class="club-list"></ol>
<div class="picker-submit">
<button type="button" class="btn-primary" id="btn-copy">Copy my code</button>
<span class="picker-status" id="copy-status"></span>
<textarea id="code-out" readonly rows="3" aria-label="Your pick code"></textarea>
<p class="note">
That single line is your whole table. Send it to Allen any way you like — text,
email, whatever. Nothing is submitted from this page.
</p>
</div>
</div>

<script>
(function () {
  var TEAMS    = PICKER_DATA.teams;
  var DEADLINE = new Date(PICKER_DATA.deadline);
  var STORE    = "eplTableBattle.draft.v1";

  var listEl   = document.getElementById("club-list");
  var nameEl   = document.getElementById("entrant");
  var codeEl   = document.getElementById("code-out");
  var saveEl   = document.getElementById("save-status");
  var copyEl   = document.getElementById("copy-status");

  // Order is held as an array of abbreviations; TEAMS is the lookup.
  var order = TEAMS.map(function (t) { return t.abbrev; });
  var byAbbrev = {};
  TEAMS.forEach(function (t) { byAbbrev[t.abbrev] = t; });

  function locked() { return new Date() >= DEADLINE; }

  /* ---- persistence ---------------------------------------------------- */

  function save() {
    try {
      localStorage.setItem(STORE, JSON.stringify({
        name: nameEl.value, order: order
      }));
      saveEl.textContent = "Draft saved";
      clearTimeout(save._t);
      save._t = setTimeout(function () { saveEl.textContent = ""; }, 1600);
    } catch (e) {
      saveEl.textContent = "Could not save a draft in this browser";
    }
  }

  function restore() {
    try {
      var raw = localStorage.getItem(STORE);
      if (!raw) return;
      var d = JSON.parse(raw);
      if (d.name) nameEl.value = d.name;
      // Only trust a stored order that is still exactly the 20 current clubs.
      if (Array.isArray(d.order) && d.order.length === TEAMS.length &&
          d.order.every(function (a) { return byAbbrev[a]; }) &&
          new Set(d.order).size === TEAMS.length) {
        order = d.order;
      }
    } catch (e) { /* corrupt draft: fall back to the default order */ }
  }

  /* ---- rendering ------------------------------------------------------ */

  function render() {
    listEl.innerHTML = "";
    order.forEach(function (abbrev, i) {
      var t  = byAbbrev[abbrev];
      var li = document.createElement("li");
      li.className = "club-item";
      li.draggable = !locked();
      li.dataset.index = i;

      li.innerHTML =
        '<span class="club-pos">' + (i + 1) + '</span>' +
        '<span class="club-grip" aria-hidden="true">⠿</span>' +
        '<span class="club-name">' + t.name + '</span>' +
        '<span class="club-nudge">' +
          '<button type="button" class="nudge" data-dir="-1" ' +
            (i === 0 ? "disabled" : "") + ' aria-label="Move ' + t.name + ' up">▲</button>' +
          '<button type="button" class="nudge" data-dir="1" ' +
            (i === order.length - 1 ? "disabled" : "") +
            ' aria-label="Move ' + t.name + ' down">▼</button>' +
        '</span>';

      listEl.appendChild(li);
    });
    updateCode();
  }

  function move(from, to) {
    if (to < 0 || to >= order.length) return;
    var item = order.splice(from, 1)[0];
    order.splice(to, 0, item);
    render();
    save();
  }

  /* ---- the code ------------------------------------------------------- */

  function slug(s) {
    return (s || "").toLowerCase().replace(/[^a-z0-9]+/g, "");
  }

  function updateCode() {
    // The name is carried through verbatim so the site can show "Sam O'Neill"
    // rather than a squashed key; the decoder derives the key itself.
    var typed = (nameEl.value || "").trim().replace(/[:\n]+/g, " ");
    codeEl.value = slug(typed)
      ? typed + ":" + order.join(",")
      : "(type your name above to generate your code)";
  }

  /* ---- events --------------------------------------------------------- */

  listEl.addEventListener("click", function (e) {
    var btn = e.target.closest(".nudge");
    if (!btn || locked()) return;
    var i = +btn.closest(".club-item").dataset.index;
    move(i, i + (+btn.dataset.dir));
  });

  var dragFrom = null;

  listEl.addEventListener("dragstart", function (e) {
    var li = e.target.closest(".club-item");
    if (!li || locked()) return;
    dragFrom = +li.dataset.index;
    li.classList.add("dragging");
    e.dataTransfer.effectAllowed = "move";
    // Firefox will not start a drag without payload.
    e.dataTransfer.setData("text/plain", String(dragFrom));
  });

  listEl.addEventListener("dragover", function (e) {
    if (dragFrom === null) return;
    e.preventDefault();
    var li = e.target.closest(".club-item");
    if (!li) return;
    var over = +li.dataset.index;
    if (over !== dragFrom) {
      var item = order.splice(dragFrom, 1)[0];
      order.splice(over, 0, item);
      dragFrom = over;
      render();
      listEl.children[over].classList.add("dragging");
    }
  });

  listEl.addEventListener("dragend", function () {
    dragFrom = null;
    render();
    save();
  });

  nameEl.addEventListener("input", function () { updateCode(); save(); });

  document.getElementById("btn-shuffle").addEventListener("click", function () {
    if (locked()) return;
    for (var i = order.length - 1; i > 0; i--) {
      var j = Math.floor(Math.random() * (i + 1));
      var tmp = order[i]; order[i] = order[j]; order[j] = tmp;
    }
    render(); save();
  });

  document.getElementById("btn-alpha").addEventListener("click", function () {
    if (locked()) return;
    order.sort(function (a, b) {
      return byAbbrev[a].name.localeCompare(byAbbrev[b].name);
    });
    render(); save();
  });

  document.getElementById("btn-reset").addEventListener("click", function () {
    if (locked()) return;
    if (!confirm("Clear your draft and start from the default order?")) return;
    order = TEAMS.map(function (t) { return t.abbrev; });
    nameEl.value = "";
    try { localStorage.removeItem(STORE); } catch (e) {}
    render();
  });

  document.getElementById("btn-copy").addEventListener("click", function () {
    if (!slug(nameEl.value)) {
      copyEl.textContent = "Add your name first.";
      nameEl.focus();
      return;
    }
    var done = function () {
      copyEl.textContent = "Copied — now send it to Allen.";
      setTimeout(function () { copyEl.textContent = ""; }, 4000);
    };
    if (navigator.clipboard && window.isSecureContext) {
      navigator.clipboard.writeText(codeEl.value).then(done, function () {
        codeEl.select(); copyEl.textContent = "Press ⌘C to copy.";
      });
    } else {
      codeEl.select();
      try { document.execCommand("copy"); done(); }
      catch (e) { copyEl.textContent = "Press ⌘C to copy."; }
    }
  });

  /* ---- go ------------------------------------------------------------- */

  restore();
  render();

  if (locked()) {
    document.getElementById("picker").classList.add("is-locked");
    ["btn-shuffle", "btn-alpha", "btn-reset", "btn-copy"].forEach(function (id) {
      document.getElementById(id).disabled = true;
    });
    nameEl.disabled = true;
  }
})();
</script>

<p class="note">
Everything here happens in your browser — your draft never leaves this device
until you send the code yourself. The page stops accepting changes after the
deadline, but that check uses your device's clock, so the entry that actually
counts is the one Allen has in hand when the table is frozen.
</p>
