---
title: "Make Your Picks"
---

```{r, child="_setup.Rmd"}
```

```{r banner, results='asis'}
cat(as.character(lock_banner()))
```

Drag the clubs into the order you think they will finish, or nudge them with the
arrows. Your draft saves in this browser as you go, so you can close the tab and
come back to it.
`r if (submissions_closed()) "The picker stays fully usable after the deadline so it can be shown to people \u2014 build a table, hit **Copy my code**, see what an entry looks like." else "When the table looks right, hit **Copy my code** at the bottom and send that one line to the Commissioner."`

```{r inject, results='asis'}
# The club list and the deadline come from the same files the rest of the site
# uses, so the picker can never drift out of sync with data/teams.csv.
payload <- list(
  teams = lapply(seq_len(nrow(TEAMS)), function(i) {
    list(name = TEAMS$team[i], abbrev = TEAMS$abbrev[i], short = TEAMS$short_name[i])
  }),
  deadline = format(CONFIG$submission_deadline, "%Y-%m-%dT%H:%M:%S%z"),
  locked = submissions_closed()
)
cat("<script>\nconst PICKER_DATA = ",
    jsonlite::toJSON(payload, auto_unbox = TRUE), ";\n</script>\n", sep = "")
```

<!-- NOTE: this block must stay flush-left. Indenting raw HTML by four spaces
makes pandoc treat it as a markdown code block and render the controls as
escaped text instead of a form. -->
<div id="picker">
<div class="picker-row">
<label for="entrant"><strong>Your name</strong></label>
<input type="text" id="entrant" placeholder="e.g. Elliot Anderson" autocomplete="name">
</div>
<div class="picker-actions">
<button type="button" class="btn-secondary" id="btn-shuffle">Shuffle</button>
<button type="button" class="btn-secondary" id="btn-alpha">A–Z</button>
<button type="button" class="btn-secondary" id="btn-reset">Start over</button>
<span class="picker-status" id="save-status"></span>
</div>
<ol id="club-list" class="club-list"></ol>
<div class="picker-submit">
<button type="button" class="btn-primary" id="btn-copy">Copy my code</button>
<span class="picker-status" id="copy-status"></span>
<textarea id="code-out" readonly rows="3" aria-label="Your pick code"></textarea>
<p class="note">
That single line is a whole table in one line. **Nothing is submitted from this
page** — a code only counts once the Commissioner has it in hand.
</p>
</div>
</div>

<script>
(function () {
  var TEAMS    = PICKER_DATA.teams;
  var DEADLINE = new Date(PICKER_DATA.deadline);
  var STORE    = "eplTableBattle.draft.v1";

  var listEl   = document.getElementById("club-list");
  var nameEl   = document.getElementById("entrant");
  var codeEl   = document.getElementById("code-out");
  var saveEl   = document.getElementById("save-status");
  var copyEl   = document.getElementById("copy-status");

  // Order is held as an array of abbreviations; TEAMS is the lookup.
  var order = TEAMS.map(function (t) { return t.abbrev; });
  var byAbbrev = {};
  TEAMS.forEach(function (t) { byAbbrev[t.abbrev] = t; });

  // Whether entries are closed. This governs what the page SAYS, not what it
  // lets you do -- past the deadline the picker still works as a demo, it just
  // stops pretending the code counts for anything.
  function entriesClosed() { return new Date() >= DEADLINE; }

  /* ---- persistence ---------------------------------------------------- */

  function save() {
    try {
      localStorage.setItem(STORE, JSON.stringify({
        name: nameEl.value, order: order
      }));
      saveEl.textContent = "Draft saved";
      clearTimeout(save._t);
      save._t = setTimeout(function () { saveEl.textContent = ""; }, 1600);
    } catch (e) {
      saveEl.textContent = "Could not save a draft in this browser";
    }
  }

  function restore() {
    try {
      var raw = localStorage.getItem(STORE);
      if (!raw) return;
      var d = JSON.parse(raw);
      if (d.name) nameEl.value = d.name;
      // Only trust a stored order that is still exactly the 20 current clubs.
      if (Array.isArray(d.order) && d.order.length === TEAMS.length &&
          d.order.every(function (a) { return byAbbrev[a]; }) &&
          new Set(d.order).size === TEAMS.length) {
        order = d.order;
      }
    } catch (e) { /* corrupt draft: fall back to the default order */ }
  }

  /* ---- rendering ------------------------------------------------------ */

  function render() {
    listEl.innerHTML = "";
    order.forEach(function (abbrev, i) {
      var t  = byAbbrev[abbrev];
      var li = document.createElement("li");
      li.className = "club-item";
      li.draggable = true;
      li.dataset.index = i;

      li.innerHTML =
        '<span class="club-pos">' + (i + 1) + '</span>' +
        '<span class="club-grip" aria-hidden="true">⠿</span>' +
        '<span class="club-name">' + t.name + '</span>' +
        '<span class="club-nudge">' +
          '<button type="button" class="nudge" data-dir="-1" ' +
            (i === 0 ? "disabled" : "") + ' aria-label="Move ' + t.name + ' up">▲</button>' +
          '<button type="button" class="nudge" data-dir="1" ' +
            (i === order.length - 1 ? "disabled" : "") +
            ' aria-label="Move ' + t.name + ' down">▼</button>' +
        '</span>';

      listEl.appendChild(li);
    });
    updateCode();
  }

  function move(from, to) {
    if (to < 0 || to >= order.length) return;
    var item = order.splice(from, 1)[0];
    order.splice(to, 0, item);
    render();
    save();
  }

  /* ---- the code ------------------------------------------------------- */

  function slug(s) {
    return (s || "").toLowerCase().replace(/[^a-z0-9]+/g, "");
  }

  function updateCode() {
    // The name is carried through verbatim so the site can show "Sam O'Neill"
    // rather than a squashed key; the decoder derives the key itself.
    var typed = (nameEl.value || "").trim().replace(/[:\n]+/g, " ");
    codeEl.value = slug(typed)
      ? typed + ":" + order.join(",")
      : "(type your name above to generate your code)";
  }

  /* ---- events --------------------------------------------------------- */

  listEl.addEventListener("click", function (e) {
    var btn = e.target.closest(".nudge");
    if (!btn) return;
    var i = +btn.closest(".club-item").dataset.index;
    move(i, i + (+btn.dataset.dir));
  });

  var dragFrom = null;

  listEl.addEventListener("dragstart", function (e) {
    var li = e.target.closest(".club-item");
    if (!li) return;
    dragFrom = +li.dataset.index;
    li.classList.add("dragging");
    e.dataTransfer.effectAllowed = "move";
    // Firefox will not start a drag without payload.
    e.dataTransfer.setData("text/plain", String(dragFrom));
  });

  listEl.addEventListener("dragover", function (e) {
    if (dragFrom === null) return;
    e.preventDefault();
    var li = e.target.closest(".club-item");
    if (!li) return;
    var over = +li.dataset.index;
    if (over !== dragFrom) {
      var item = order.splice(dragFrom, 1)[0];
      order.splice(over, 0, item);
      dragFrom = over;
      render();
      listEl.children[over].classList.add("dragging");
    }
  });

  listEl.addEventListener("dragend", function () {
    dragFrom = null;
    render();
    save();
  });

  nameEl.addEventListener("input", function () { updateCode(); save(); });

  document.getElementById("btn-shuffle").addEventListener("click", function () {
    for (var i = order.length - 1; i > 0; i--) {
      var j = Math.floor(Math.random() * (i + 1));
      var tmp = order[i]; order[i] = order[j]; order[j] = tmp;
    }
    render(); save();
  });

  document.getElementById("btn-alpha").addEventListener("click", function () {
    order.sort(function (a, b) {
      return byAbbrev[a].name.localeCompare(byAbbrev[b].name);
    });
    render(); save();
  });

  document.getElementById("btn-reset").addEventListener("click", function () {
    if (!confirm("Clear your draft and start from the default order?")) return;
    order = TEAMS.map(function (t) { return t.abbrev; });
    nameEl.value = "";
    try { localStorage.removeItem(STORE); } catch (e) {}
    render();
  });

  document.getElementById("btn-copy").addEventListener("click", function () {
    if (!slug(nameEl.value)) {
      copyEl.textContent = "Add your name first.";
      nameEl.focus();
      return;
    }
    // Both the success and the manual-fallback message have to respect the
    // deadline, or someone demoing the page is told to send in a code that
    // will not be counted.
    var tail = entriesClosed()
      ? "demo only, this will not be entered."
      : "now send it to the Commissioner.";
    var done = function () {
      copyEl.textContent = "Copied — " + tail;
      setTimeout(function () { copyEl.textContent = ""; }, 5000);
    };
    var manual = function () {
      codeEl.select();
      copyEl.textContent = "Press ⌘C to copy — " + tail;
    };
    if (navigator.clipboard && window.isSecureContext) {
      navigator.clipboard.writeText(codeEl.value).then(done, manual);
    } else {
      codeEl.select();
      try { document.execCommand("copy"); done(); }
      catch (e) { manual(); }
    }
  });

  /* ---- go ------------------------------------------------------------- */

  restore();
  render();

  if (entriesClosed()) {
    var note = document.createElement("p");
    note.className = "note demo-note";
    note.innerHTML = "<strong>Entries are closed.</strong> The picker below still " +
      "works \u2014 but a code generated now " +
      "is a demonstration and will not be entered.";
    var host = document.getElementById("picker");
    host.parentNode.insertBefore(note, host);
  }
})();
</script>

<p class="note">
Everything here happens in your browser — your draft never leaves this device
until you send the code yourself. 
</p>
