---
title: "Rules"
---

```{r, child="_setup.Rmd"}
```

## The competition

Each entrant submits one complete ordering of all `r nrow(TEAMS)` Premier League
clubs — their guess at the final `r CONFIG$season_label` table, from champion to
bottom. No partial entries, no ties, every club used exactly once.

## The deadline

Entries `r if (is_locked()) "were due" else "are due"`
**`r fmt_when(CONFIG$lock_time)`**.

At that instant `data/predictions.csv` is snapshotted to
`data/predictions_frozen.csv`, and every build after the deadline renders the
snapshot rather than the working file. If the working file is edited afterwards the build emits a warning and
ignores the change, so a late edit cannot quietly reach the site.

## Scoring

```{r scoring-desc, results='asis'}
cat(describe_method())
```

**Currently active rule:** `` `r CONFIG$scoring_method` `` —
`r if (score_direction() == "lower") "lowest total wins" else "highest total wins"`.

Ties are broken by (1) more exact positions called, then (2) a smaller worst
single miss.

### Worked example

```{r example}
ex <- tibble::tibble(
  Club = c("Liverpool", "Arsenal", "Everton"),
  Picked = c(1L, 2L, 12L),
  Actual = c(1L, 4L, 9L)
) |> dplyr::mutate(
  `Off by` = abs(Picked - Actual),
  Score = SCORERS[[CONFIG$scoring_method]](
    data.frame(predicted = Picked, actual = Actual)
  )
)
knitr::kable(ex, align = c("l", "r", "r", "r", "r")) |>
  kableExtra::kable_styling(bootstrap_options = c("striped"), full_width = FALSE)
```

Across three clubs that entrant would score
`r sum(SCORERS[[CONFIG$scoring_method]](data.frame(predicted = c(1L,2L,12L), actual = c(1L,4L,9L))))`.
The real thing runs over all `r nrow(TEAMS)`.

<p class="note">
The points method is still being finalised. Changing it means editing one line —
<code>scoring_method</code> in <code>R/config.R</code> — or adding a function to
<code>SCORERS</code> in <code>R/scoring.R</code>. Every page recalculates from
whatever is set there; nothing else needs touching.
</p>

## Data

The live table is pulled from ESPN's public standings endpoint each time the
site is rebuilt. It is cached to `data/live_table.csv`, so if the fetch fails the
site still builds from the last good snapshot and says so.

## The clubs

```{r clubs}
TEAMS |>
  dplyr::transmute(Club = team, `Also accepted as` = gsub("|", ", ", aliases, fixed = TRUE)) |>
  knitr::kable(align = c("l", "l")) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"),
                            full_width = TRUE, font_size = 12)
```
