---
title: "Rules"
---

```{r, child="_setup.Rmd"}
```

## The competition

Each entrant submits one complete ordering of all `r nrow(TEAMS)` Premier League
clubs — their guess at the final `r CONFIG$season_label` table, from champion to
bottom. No partial entries, no ties, every club used exactly once.

## The deadline

Entries `r if (is_locked()) "were due" else "are due"`
**`r fmt_when(CONFIG$lock_time)`**.

At that instant `data/predictions.csv` is snapshotted to
`data/predictions_frozen.csv`, and every build after the deadline renders the
snapshot rather than the working file. If the working file is edited afterwards the build emits a warning and
ignores the change, so a late edit cannot quietly reach the site.

## Scoring

```{r scoring-desc, results='asis'}
cat(describe_method())

# **Currently active rule:** `` `r CONFIG$scoring_method` `` —
# `r if (score_direction() == "lower") "lowest total wins" else "highest total wins"`.
```

Ties are broken by (1) more exact positions called, then (2) a smaller worst
single miss.

### When scoring opens

Every total reads **0 until `r fmt_when(CONFIG$scoring_start)`**, however the
league table looks before then.
`r if (scoring_active()) "That moment has passed, so points are live." else "That moment has not arrived yet."`

## Bonuses

Bonuses are awarded **on top of** the per-club points, and only in the final
week of the season — from **`r fmt_when(CONFIG$bonus_start)`**.
`r if (bonuses_active()) "They are currently included in every total." else "They are not in play yet, so totals on the front page are per-club points only."`

```{r bonus-table}
tibble::tibble(
  Bonus = c("Champion",
            "Relegated three",
            "Champions League places",
            "Relegation places"),
  Award = c(sprintf("+%d", CONFIG$bonus_champion),
            sprintf("+%d", CONFIG$bonus_relegation_set),
            sprintf("+%d each", CONFIG$bonus_ucl_each),
            sprintf("+%d each", CONFIG$bonus_relegation_each)),
  Maximum = c(CONFIG$bonus_champion,
              CONFIG$bonus_relegation_set,
              CONFIG$bonus_ucl_each * CONFIG$ucl_places,
              CONFIG$bonus_relegation_each * CONFIG$relegation_places),
  `What it takes` = c(
    "You put the eventual champion 1st.",
    sprintf("The three clubs you placed %d–%d are exactly the three that go down, in any order.",
            nrow(TEAMS) - CONFIG$relegation_places + 1, nrow(TEAMS)),
    sprintf("For each club you placed in the top %d that finishes in the top %d.",
            CONFIG$ucl_places, CONFIG$ucl_places),
    sprintf("For each club you placed in the bottom %d that finishes in the bottom %d.",
            CONFIG$relegation_places, CONFIG$relegation_places))
) |>
  knitr::kable(align = c("l", "c", "c", "l")) |>
  kableExtra::kable_styling(bootstrap_options = c("striped"), full_width = TRUE)
```

Maximum possible bonus:
**+`r CONFIG$bonus_champion + CONFIG$bonus_relegation_set + CONFIG$bonus_ucl_each * CONFIG$ucl_places + CONFIG$bonus_relegation_each * CONFIG$relegation_places`**,
for a perfect-table ceiling of
**`r max_club_points() * nrow(TEAMS) + CONFIG$bonus_champion + CONFIG$bonus_relegation_set + CONFIG$bonus_ucl_each * CONFIG$ucl_places + CONFIG$bonus_relegation_each * CONFIG$relegation_places`**.

The bonuses stack deliberately. Calling the champion correctly earns the
+`r CONFIG$bonus_champion` champion bonus *and* one Champions League place point,
so it is worth +`r CONFIG$bonus_champion + CONFIG$bonus_ucl_each` in total.
Naming all three relegated clubs earns the
+`r CONFIG$bonus_relegation_set` set bonus *and*
`r CONFIG$relegation_places` relegation place points, so
+`r CONFIG$bonus_relegation_set + CONFIG$bonus_relegation_each * CONFIG$relegation_places`.

### Worked example

```{r example}
ex <- tibble::tibble(
  Club = c("Liverpool", "Arsenal", "Everton"),
  Picked = c(1L, 2L, 12L),
  Actual = c(1L, 4L, 9L)
) |> dplyr::mutate(
  `Off by` = abs(Picked - Actual),
  Score = SCORERS[[CONFIG$scoring_method]](
    data.frame(predicted = Picked, actual = Actual)
  )
)
knitr::kable(ex, align = c("l", "r", "r", "r", "r")) |>
  kableExtra::kable_styling(bootstrap_options = c("striped"), full_width = FALSE)
```

Across three clubs that entrant would score
`r sum(SCORERS[[CONFIG$scoring_method]](data.frame(predicted = c(1L,2L,12L), actual = c(1L,4L,9L))))`.
The real thing runs over all `r nrow(TEAMS)` clubs.

```{r include = FALSE}
#<p class="note">
#The points method is still being finalised. Changing it means editing one line —
#<code>scoring_method</code> in <code>R/config.R</code> — or adding a function to
#<code>SCORERS</code> in <code>R/scoring.R</code>. Every page recalculates from
#whatever is set there; nothing else needs touching.
#</p>
```


## Data

The live table is pulled from
**`r provider_label(attr(LIVE, "provider"))`** each time the site is rebuilt. It is cached to `data/live_table.csv`, so if both fail the site still
builds from the last good snapshot and says so on the front page. Refresh your cache or reach out to the Commissioner if the data seems off.
